\documentclass[a4paper,11pt,runningheads]{llncs}

%\usepackage[margin=2.7cm]{geometry}

\pdfpagewidth=210 true mm
\pdfpageheight=297 true mm

\usepackage[table]{xcolor}
\definecolor{linkcolor}{rgb}{0.65,0,0}
\definecolor{citecolor}{rgb}{0,0.65,0}
\definecolor{urlcolor}{rgb}{0,0,0.65}
\usepackage[breaklinks=true,colorlinks=true, backref=page, linkcolor=linkcolor, urlcolor=urlcolor, citecolor=citecolor]{hyperref}
\usepackage{hyperref}

\usepackage{amsfonts,amsmath,amscd,amssymb,array}
\usepackage{algorithm, algpseudocode}
\usepackage{tabularx,booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{float}
\floatname{listing}{Listing}

\input{macros}



\begin{document}

\titlerunning{Multi-Scalar Multiplication Using DBNS }
\title{Fast Elliptic Curve Multi-Scalar Multiplication Using DBNS with Constant Number of Pre-Computation Points}
\authorrunning{C. Chuengsatiansup, V. Suppakitpaisarn}

\author{
Chitchanok Chuengsatiansup\inst{1}
\thanks{This work was supported by the Netherlands Organisation for Scientific Research (NWO) under grant 639.073.005.}
\and
Vorapong Suppakitpaisarn\inst{2}
}

\institute{
Department of Mathematics and Computer Science \\
Technische Universiteit Eindhoven\\
P.O. Box 513, 5600 MB Eindhoven, the Netherlands\\
\email{c.chuengsatiansup@tue.nl}
\and
National Institute of Informatics\\
2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo, 101-8430, Japan\\
\email{vorapong@nii.ac.jp}
}

\maketitle

\begin{abstract}
In this paper, we propose a fast algorithm for an elliptic curve multi-scalar multiplication based on the number representation called double-based number system (DBNS). As a method based on the representation is known to be one of the fastest algorithms up to date, DBNS is one of the tools used for reducing the computation time of a scalar multiplication.  A weak point of the DBNS-based scalar multiplication is its memory consumption. In the worst case, the method require us to store almost $n$ pre-computation points during its process.  We propose a method that can reduce the memory consumption in this paper. Using the same number of pre-computation points, the computation time of our multi-scalar multiplication is smaller than those of a sliding window method and a double-base chain representation. Beside a greedy heuristic algorithm, we also give an algorithm that can optimize the computation time in this setting. Our analysis shows that, when using the same number of pre-computation points, our optimal computation time is much smaller than the previous method. 

\smallskip
\textbf{Keywords:} 
elliptic curve, double-base number system, multi-scalar multiplication, interleaving method, optimal algorithm
\end{abstract}

\input{intro}
\input{interleave}
\input{optimal}
\input{conclusion}

\clearpage
\bibliographystyle{plain}
\bibliography{collection}

\end{document}
